### 2011-09-29 doc/manuscript.tex
Just an update.

@@

\subsection{The virulence genes}
\texttt{Find cases of any virulence genes that were transferred via recombining and
horizontally.} 
\texttt{I need to see how the virulence genes list was created.}
\texttt{I want to know the virulence gene categories. Which kind of virulence
genes are more under gene transfer?}
\texttt{Make a list of virulence genes and their categories with more
interpretations.}

@@

\subsection{Comparison between model-based and parsimony-based approaches}
\texttt{I might want to analyze using only core genomes and pan genomes
separately. By separating data set of 6-gene families from the other families,
we could have more complete comparison.}

@@

\subsection{Functional categories associated with gene transfer}

Table \ref{tab:functional} lists the functional categories that showed
significantly associated with recombination intensity. 
Several functional categories are related with ribosomes.
There was a functional category related with phosphotransferase systems
and ATP-binding cassette (ABC) transporters, i.e., carbohydrate transport
(GO:0008643). Translation (GO:0006412) included aminoacyl tRNA synthetase.
There were fatty acid biosynthetic process (GO:0006633) and lipid
biosynthetic process (GO:0008610). We did not find any significant association 
between recombination intensity and virulence genes. When measuring 
recombination only between the SDE and SPY clades, a smaller number of 
functional categories appeared to be significantly enriched, leaving the two 
biosynthetic processes out. For the direction from SPY to SDE only transport 
related
functional categories appeared to be significant, leaving out ribosome related 
functional categories and translation.

%\textbf{Functional categories associated with non-recombining gene transfer:}

Table \ref{tab:go-events} lists the functional gene categories that
showed significantly associated with gene duplications, losses,
non-recombining and recombining gene transfer using the pan genome of the six
\textit{Streptococcus} individuals.

For the recombining transfers, Mowgli shows enrichment in
many of the same categories as \texttt{ClonalOrigin}, such as translation,
ribosome, and rRNA binding.  This agreement between the two different
methods, applied on somewhat different parts of the data, serves as
validation for the signal picked up by these separate association
studies.

However, for duplication, losses, and non-recombining
transfers, we find enrichment in very different categories related to
transposition, integration, and recombination.  Interestingly, gene
duplication and non-recombining transfers show enrichment in the same
categories, perhaps because both mechanisms increase gene copy number.
Gene losses also showed enrichment for transposition and integration,
but less significantly ($P<10^{-6}$) and also showed enrichment for
several additional categories such as transporter activity and
transcription initiation.  Unlike the associations with recombination
intensity, families with high numbers of duplications and
non-recombining gene transfer were significantly enriched for
virulence ($P<7.13 \times 10^{-3}$ and $P<1.33 \times 10^{-11}$,
respectively), whereas families with high losses and recombination
showed no enrichment ($P>0.54$ and $P>0.90$).  This might indicate
that non-recombining gene transfer served as a more effective means by
which SDE or SPY acquired virulence genes, compared to recombining
gene transfer.

\texttt{NEXT PARAGRAPH CONTAINS RESULTS ON INFERENCE OF SPECIFIC TRANSFER 
EVENTS. WE SHOULD DECIDE HOW TO RELATE THIS TO OUR OTHER RESULTS.}

%\textbf{Some detailed gene-level analyses:}
Having found these functional categories, we elected to search for specific 
genes that showed a clear and specific local signal of recombination.  We scanned 
all 274 alignment blocks to locate parts of genes for which a recombinant edge 
of a certain type was sampled with probability at least 0.9. 
% We focused on specific types of recombinant edges 
% \texttt{IG: ADD A BIT HERE. SC: I DO NOT SEE WHAT IG MEANT.}
We found a total of 58 genes showing high-confidence local 
recombination signal (Table S\ref{tab:genes-transfer}). The process of gene 
transfer does not necessarily move whole genes from one species to another 
\citep[e.g.,][]{Chan2009}, and we observed that units of 
recombining gene transfer do 
not correspond to single genes in their entirety. In some cases, only parts of 
a gene were inferred to have been transferred, for instance, transfer from SPY1 
to SDE1 was inferred for 29\% of the aspartyl-tRNA synthetase gene (see also 
Figure S\ref{fig:muts}). In other cases, the inferred transfer units cover sets 
of as much as eight adjacent genes.

%Not only parts of genes could be transferred via recombination, but a group of 
%genes could also be moved together. Of the genes listed in Table 
%S\ref{tab:genes-transfer} there were 12 groups of genes that were consecutive. 
%While transfer fragments of genes often covered two genes, there were transfer 
%fragments that covered eight genes together. Loci from SpyM3\_1512 to 
%SpyM3\_1525 were inferred to be transferred from SDE2 to SDD.

@@

>>>>

Furthermore, we found a total of 58 genes 
for which a recombinant edge 
of certain types were sampled with probability at least 0.9
by focusing on specific types of recombinant edges.
(Table S\ref{tab:genes-transfer}).  Many of the genes in the list were
transferred from SPY to SDE rather than the reverse direction overall.

@@

\subsection{The virulence genes}
\texttt{Find cases of any virulence genes that were transferred via recombining and
horizontally.} 
\texttt{I need to see how the virulence genes list was created.}
\texttt{I want to know the virulence gene categories. What kind of virulence
genes are more under gene transfer?}
\texttt{Make a list of virulence genes and their categories with more
interpretations.}

A list of virulence genes that might be transferred via recombining gene
transfer.
block 76: SDEG\_0641
block 97: SDEG\_0673
block 101: SDEG\_0739
block 151: SDEG\_1447
block 244: SDEG\_2040
block 242: SDD27957\_00955
block 240: SDD27957\_00985
block 67: SDD27957\_03085
block 133: SDD27957\_04505
block 167: SDD27957\_06790
block 170: SDD27957\_07725
block 186: MGAS10750\_Spy1444
block 255: MGAS10750\_Spy1922

Blocks with virulence genes.

Check virulence genes (they were combined) at 
SDD27957\_02890, SDD27957\_02895
MGAS10750\_Spy0455, MGAS10750\_Spy0456 (block 75)

@@

\subsection{Comparison between model-based and parsimony-based approaches}
\texttt{I might want to analyze only core genomes and pan genomes
separately. By separating data set of 6-gene families from the other families,
we could have more complete comparison.}

@@

\subsection{Transporter and aminoacyl tRNA synthetases}
Lateral transfer of transporter related genes are well known.  Functional
categories associated with higher recombining gene transfer were found to
include phosphotransferase systems and ATP-binding cassette (ABC) transporters,
i.e., carbohydrate transport (GO:0008643) (Table \ref{tab:functional}).  We also
found several aminoacyl tRNA synthetases in gene ontology of translation
(GO:0006412) to be significantly associated with higher recombining gene
transfer.  Note that functional categories concerning ribosomes were also
associated with higher recombining gene transfer. These categories were not
found significantly associated with higher recombining gene transfer when we
considered only gene transfer between SPY and SDE genomes, which implied that
many recombining gene transfer events should be attributed to those of internal
species branches as donors.  Interestingly, transports functional categories
were found to be associated with recombining gene transfer for the direction
from SPY to SDE.  The parsimony-based approach also  shows enrichment of the
recombining transfers in many of the same categories such as translation,
ribosome, and rRNA binding (Table \ref{tab:go-events}).  This agreement between
the two different methods, applied on somewhat different parts of the data,
serves as validation for the signal picked up by these separate association
studies.  
\texttt{Comparison of Mawgli and CO?}
Recombining gene transfers were not enriched for virulence genes (P-value of $>0.90$)
while horizontal gene transfers were found to be significantly associated with
virulence genes (P-value of $<1.33 \times 10^{-11}$). This was also consistent
with the fact that we could not find the association of recombining gene
transfer with virulence genes in the model-based approach.
This supported more evidence
that non-recombining gene transfer served as a more effective means by
which SDE or SPY acquired virulence genes, compared to recombining
gene transfer.
For horizontal gene transfer we found enrichment in very different 
categories related to
transposition, integration, and recombination.  
\texttt{More interpretations about Mawgli analsis of function categories?}

Gene duplication and loss events were enriched for categories similar to those
of horizontal gene transfer's enrichment.  Interestingly, gene duplication and
horizontal transfers showed enrichment in the same categories, perhaps because
both mechanisms increase gene copy number.  Gene losses showed enrichment
for transposition and integration, but less significantly (P-value of
$<10^{-6}$), and showed enrichment for several additional categories such as
transporter activity and transcription initiation.  Families with high numbers
of duplications were significantly enriched for virulence genes (P-value of
$<7.13 \times 10^{-3}$), whereas families with high losses showed no enrichment
(P-value of $>0.54$).

@@

\subsection{Units of recombining gene transfer}
The process of gene 
transfer does not necessarily move whole genes from one species to another 
\citep[e.g.,][]{Chan2009}, and we observed that units of 
recombining gene transfer do 
not correspond to single genes in their entirety
(Table S\ref{tab:genes-transfer}). In some cases, only parts of 
a gene were inferred to have been transferred, for instance, transfer from SPY1 
to SDE1 was inferred for 29\% of the aspartyl-tRNA synthetase gene (see also 
Figure S\ref{fig:muts}). In other cases, the inferred transfer units cover sets 
of as much as eight adjacent genes.
Not only parts of genes could be transferred via recombination, but a group of 
genes could also be moved together. Of the genes listed in Table 
S\ref{tab:genes-transfer} there were 12 groups of genes that were consecutive. 
While transfer fragments of genes often covered two genes, there were transfer 
fragments that covered eight genes together. Loci from SpyM3\_1512 to 
SpyM3\_1525 were inferred to be transferred from SDE2 to SDD.
